---
title: "Problem 2"
author: "Glen Miasnychenko"
date: "2023-09-07"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Here is my code for the second problem of the second homework.

### Problem 2 - A

```{r cars}
library(readxl)
file_path <- "~/Downloads/FreshDetergent.xlsx"
FreshDetergent <- read_excel(file_path)
attach(FreshDetergent)
#Demand = beta0+beta1*PriceDif+error
result=lm(Demand ~ PriceDif)
summary(result)
```


### Problem 2 - B

We can identify the estimates for Beta0 and Beta1, using the output above. In
particular, we have to look for the *Estimate* column in the table. From there we get:

**Estimate for Beta0** = 7.81409  
**Estimate for Beta1** = 2.66521

### Problem 2 - C

The table does not contain information for all of the required statistics. What it does
contain is the *MSE* (also known as *Residual Standard error*) and *degrees of freedom*.  

With that information we can calculate everything we need:  

**SSE** = MSE * df = 0.3166*28 = 8.8648.   
**s^2** = MSE = 0.3166.   
**s** = sqrt(0.3166) = 0.5626722.   

### Problem 2 - D

The values for T-test on Beta1 can be found in the *PriceDif* string of the initial table.
From there we get:

**t(Beta1)** = 10.31.   
**Pr(>|t|)** = 4.88e-11.   

With Alpha = 0.05, we have to reject the Null Hypothesis, since p<Alpha. Therefore our model fits the data.

### Problem 2 - E
```{r}
confint(result, level = 0.95)
```

Therefore the CI for Beta1 is (2.135702; 3.194727).

### Problem 2 - F

The values for T-test on Beta0 can be found in the *Intercept* string of the initial table.
From there we get:

**t(Beta0)** = 97.82.     
**Pr(>|t|)** = 2e-16. 

With Alpha = 0.05, we have to reject the Null Hypothesis, since p<Alpha.Therefore, our model fits the data.

### Problem 2 - G
```{r}
new.dat <- data.frame(PriceDif=0.1)
predict(result, newdata = new.dat, interval = 'confidence', level = 0.95)
predict(result, newdata = new.dat, interval = 'prediction', level = 0.95)
```

### Problem 2 - H

We know that **simple coefficient of determination** = r^2, and it can be found in the 
original table. From there we know r^2 = 0.7915. This means that 0.7915 of variance of 
the dependent variable is explained by the model.         

Then, we can use unexplained variation from the part C:   
**Sum of Squares of Error** = SSE = 8.8648.      

In order to find the **Sum of Squares of Regression**, we will use the formula for F-statistic:     
SSR =  F * (SSE/(n-2)) = 106.3 * (8.8648/28) = 335.7549.      

Therefore, the **Total Variation** = SST = SSE + SSR = 8.8648 + 335.7549 = 344.6197

### Problem 2 - I

**F-Statistic** can be found in the table. From there, F = 106.3.       
The respective **p-value** = 4.881e-11.     

Since the p-value is smaller than Alpha = 0.01, **we have to reject the Null Hypothesis. 
Therefore the model fits the data.**


### Problem 2 - J
```{r}
t_rejection_point <- qt(0.025, 28, lower.tail = FALSE)
f_rejection_point <- qf(0.05, 1, 28, lower.tail = FALSE)
t_rej_sqrd <- t_rejection_point * t_rejection_point
t_rej_sqrd
f_rejection_point
```

As we can see, the F-rejection point is equal to the T-rejection point squared. 
